(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-28 ms/ms.tex
Added VSURF for spatially-averaged climate

\begin{table}[ht]
   \centering
   \topcaption{16 Focal populations}
   \begin{tabular}{@{} lllllll @{}}
      \toprule
  Name& Region  & Demo?& Pop gen?& Latitude  & Longtiude  & Elevation (mas) \\
      \midrule
	HAU & South Margin		& yes	& yes	& 	& 
    	&    \\
	CTC	& South Margin		& yes	& no	&  & 
    	&    \\
	CUR	& South Margin		& yes	& yes &  & 
    	&    \\
	GRP & South Margin		& no	& no	&  &
    	&    \\
	WWC &	Transverse		  & yes	& yes	&  & 
    	&    \\
	MIL	& Transverse	  	& yes	& no	&  & 
    	&    \\
	WFM	& Transverse	  	& yes	& no	&  & 
    	&    \\
	NMT	& South Sierras		& yes	& yes?&  & 
    	&    \\
	PRD	& South Sierras		& yes	& yes	&  & 
    	&    \\
	RWD	& South Sierras		& yes	& yes	&  & 
    	&    \\
	WNA	& Central Sierras	& yes	& yes	&  & 
    	&    \\
	RBW	& Central Sierras	& yes	& no	&  & 
    	&    \\
	MYU	& North Sierras		& yes	& yes	&  & 
    	&    \\
	LIJ	& North Sierras		& yes	& yes	&  & 
    	&    \\
	DPC	& North Coast	  	& yes	& yes	&  & 
    	&    \\
	RCC	& North Margin		& yes	& yes	&  & 
    	&    \\
	\bottomrule
   \end{tabular}
\end{table}

@@

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in VSURF.parallel.formula(linmod.PC1, data = focClim[, c("{}PC1"{}, : VSURF with a formula-type call outputs selected variables\\\#\# which are indices of the input matrix based on the formula:\\\#\# you may reorder these to get indices of the original data}}\begin{alltt}
  \hlcom{# Plot most important climatic predictor versus PC1}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_bio16cva_v_Lat.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{5}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{5}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{))}
  \hlkwd{plot}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0.25}\hlstd{,} \hlnum{0.55}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{axes} \hlstd{= F,}
    \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Precipitation of Wettest Quarter"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"(Coefficient of variation)"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{ylab} \hlstd{=} \hlkwd{substitute}\hlstd{(}\hlkwd{plain}\hlstd{(Principal}\hlopt{~}\hlstd{Component}\hlopt{~}\hlnum{1}\hlstd{)}\hlopt{~}\hlkwd{group}\hlstd{(}\hlstr{"("}\hlstd{, x,} \hlstr{")"}\hlstd{),}
    \hlkwd{list}\hlstd{(}\hlkwc{x} \hlstd{= pve)))}
  \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlkwd{axis}\hlstd{(}\hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{,} \hlnum{2}\hlstd{),} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlstd{fitBio16cva} \hlkwb{<-} \hlkwd{lm}\hlstd{(PC1} \hlopt{~} \hlstd{bio16_cva,} \hlkwc{data} \hlstd{= focClim)}

  \hlcom{# polygon of confidence intervals}
  \hlstd{x} \hlkwb{<-} \hlkwd{seq}\hlstd{(}\hlkwd{min}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwd{max}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwc{l} \hlstd{=} \hlnum{1e3}\hlstd{)}
  \hlstd{u} \hlkwb{<-} \hlkwd{predict}\hlstd{(fitBio16cva,} \hlkwc{new} \hlstd{=} \hlkwd{data.frame}\hlstd{(}\hlkwc{bio16_cva} \hlstd{= x))}
  \hlstd{s} \hlkwb{<-} \hlkwd{sqrt}\hlstd{(}\hlkwd{sapply}\hlstd{(x,} \hlkwa{function}\hlstd{(}\hlkwc{X}\hlstd{)} \hlkwd{t}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, X))} \hlopt{%*%} \hlkwd{vcov}\hlstd{(fitBio16cva)} \hlopt{%*%} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, X)))}
  \hlstd{confInt} \hlkwb{<-} \hlkwd{data.frame}\hlstd{(}\hlkwc{lowerCI} \hlstd{=} \hlkwd{qnorm}\hlstd{(}\hlnum{0.025}\hlstd{, u, s),} \hlkwc{upperCI} \hlstd{=} \hlkwd{qnorm}\hlstd{(}\hlnum{0.975}\hlstd{, u, s))}
  \hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(x,} \hlkwd{rev}\hlstd{(x)),} \hlkwd{c}\hlstd{(confInt}\hlopt{$}\hlstd{lowerCI,} \hlkwd{rev}\hlstd{(confInt}\hlopt{$}\hlstd{upperCI)),}
    \hlkwc{col} \hlstd{=} \hlstr{"grey80"}\hlstd{,} \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{)}
  \hlkwd{lines}\hlstd{(x, confInt}\hlopt{$}\hlstd{lowerCI,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{lines}\hlstd{(x, confInt}\hlopt{$}\hlstd{upperCI,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{lines}\hlstd{(}\hlkwd{range}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwd{range}\hlstd{(}\hlkwd{predict}\hlstd{(fitBio16cva)),} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{points}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{= primShade0,}
    \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
  \hlcom{# Overlap between latitude predictors and phenotype predictors}
  \hlstd{imp2} \hlkwb{<-} \hlstd{climVars[vsurfPC1}\hlopt{$}\hlstd{varselect.pred]}
  \hlstd{nImpPC1} \hlkwb{<-} \hlkwd{length}\hlstd{(imp2)}

  \hlstd{vsurfLat}\hlopt{$}\hlstd{varselect.pred}
\end{alltt}
\begin{verbatim}
##  [1] 45 43 42 20 47 41 46 39 19 13
\end{verbatim}
\begin{alltt}
  \hlstd{imp1} \hlkwb{<-} \hlstd{climVars[vsurfLat}\hlopt{$}\hlstd{varselect.pred]}
  \hlstd{nImpLat} \hlkwb{<-} \hlkwd{length}\hlstd{(imp1)}

@@

        \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, nImpLat),}
                \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
        \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Climate-Trait PC1\textbackslash{}nImportance"}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlstd{(nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{)))}
        \hlstd{\{}
                \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{100}\hlstd{,} \hlnum{100}\hlstd{),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
        \hlstd{\}}
        \hlkwd{points}\hlstd{(vsurfPC1}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlstd{nImpPC1], nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{),}
                \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlcom{# mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, }
  \hlcom{#  at = nImpLat:(nImpLat - nImpPC1 + 1), }
        \hlcom{#	font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{,} \hlnum{0.1}\hlstd{))}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{table}[ht]
   \centering
   \topcaption{16 Focal populations}
   \begin{tabular}{@{} lllllll @{}}
      \toprule
  Name& Region  & Demo?& Pop gen?& Latitude  & Longtiude  & Elevation (mas) \\
      \midrule
	HAU & South Margin		& yes	& yes	& 32.657	& 
    \ensuremath{-116.532}	& 799   \\
	CTC	& South Margin		& yes	& no	& 32.609 & 
    \ensuremath{-116.7}	& 267   \\
	CUR	& South Margin		& yes	& yes & 32.9 & 
    \ensuremath{-116.585}	& 1180   \\
	GRP & South Margin		& no	& no	& 33.314 &
    \ensuremath{-116.871}	& 1577   \\
	WWC &	Transverse		  & yes	& yes	& 33.994 & 
    \ensuremath{-116.665}	& 705   \\
	MIL	& Transverse	  	& yes	& no	& 34.077 & 
    \ensuremath{-116.873}	& 2050   \\
	WFM	& Transverse	  	& yes	& no	& 34.284 & 
    \ensuremath{-117.378}	& 1120   \\
	NMT	& South Sierras		& yes	& yes?& 36.201 & 
    \ensuremath{-118.651}	& 1314   \\
	PRD	& South Sierras		& yes	& yes	& 36.518 & 
    \ensuremath{-118.759}	& 926   \\
	RWD	& South Sierras		& yes	& yes	& 36.691 & 
    \ensuremath{-118.91}	& 1727   \\
	WNA	& Central Sierras	& yes	& yes	& 37.541 & 
    \ensuremath{-119.649}	& 1224   \\
	RBW	& Central Sierras	& yes	& no	& 37.819 & 
    \ensuremath{-120.007}	& 876   \\
	MYU	& North Sierras		& yes	& yes	& 39.397 & 
    \ensuremath{-121.082}	& 455   \\
	LIJ	& North Sierras		& yes	& yes	& 39.743 & 
    \ensuremath{-120.704}	& 1603   \\
	DPC	& North Coast	  	& yes	& yes	& 41.668 & 
    \ensuremath{-123.11}	& 707   \\
	RCC	& North Margin		& yes	& yes	& 43.374 & 
    \ensuremath{-122.957}	& 326   \\
	\bottomrule
   \end{tabular}
\end{table}

@@

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in model.frame.default(formula = ord.sd \textasciitilde{} ., data = u, na.action = function (x) : variable lengths differ (found for 'u')}}\begin{alltt}
  \hlcom{# Plot most important climatic predictor versus PC1}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_bio16cva_v_Lat.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{5}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{5}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{))}
  \hlkwd{plot}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0.25}\hlstd{,} \hlnum{0.55}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{axes} \hlstd{= F,}
    \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Precipitation of Wettest Quarter"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"(Coefficient of variation)"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{ylab} \hlstd{=} \hlkwd{substitute}\hlstd{(}\hlkwd{plain}\hlstd{(Principal}\hlopt{~}\hlstd{Component}\hlopt{~}\hlnum{1}\hlstd{)}\hlopt{~}\hlkwd{group}\hlstd{(}\hlstr{"("}\hlstd{, x,} \hlstr{")"}\hlstd{),}
    \hlkwd{list}\hlstd{(}\hlkwc{x} \hlstd{= pve)))}
  \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlkwd{axis}\hlstd{(}\hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{,} \hlnum{2}\hlstd{),} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlstd{fitBio16cva} \hlkwb{<-} \hlkwd{lm}\hlstd{(PC1} \hlopt{~} \hlstd{bio16_cva,} \hlkwc{data} \hlstd{= focClim)}

  \hlcom{# polygon of confidence intervals}
  \hlstd{x} \hlkwb{<-} \hlkwd{seq}\hlstd{(}\hlkwd{min}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwd{max}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwc{l} \hlstd{=} \hlnum{1e3}\hlstd{)}
  \hlstd{u} \hlkwb{<-} \hlkwd{predict}\hlstd{(fitBio16cva,} \hlkwc{new} \hlstd{=} \hlkwd{data.frame}\hlstd{(}\hlkwc{bio16_cva} \hlstd{= x))}
  \hlstd{s} \hlkwb{<-} \hlkwd{sqrt}\hlstd{(}\hlkwd{sapply}\hlstd{(x,} \hlkwa{function}\hlstd{(}\hlkwc{X}\hlstd{)} \hlkwd{t}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, X))} \hlopt{%*%} \hlkwd{vcov}\hlstd{(fitBio16cva)} \hlopt{%*%} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, X)))}
  \hlstd{confInt} \hlkwb{<-} \hlkwd{data.frame}\hlstd{(}\hlkwc{lowerCI} \hlstd{=} \hlkwd{qnorm}\hlstd{(}\hlnum{0.025}\hlstd{, u, s),} \hlkwc{upperCI} \hlstd{=} \hlkwd{qnorm}\hlstd{(}\hlnum{0.975}\hlstd{, u, s))}
  \hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(x,} \hlkwd{rev}\hlstd{(x)),} \hlkwd{c}\hlstd{(confInt}\hlopt{$}\hlstd{lowerCI,} \hlkwd{rev}\hlstd{(confInt}\hlopt{$}\hlstd{upperCI)),}
    \hlkwc{col} \hlstd{=} \hlstr{"grey80"}\hlstd{,} \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{)}
  \hlkwd{lines}\hlstd{(x, confInt}\hlopt{$}\hlstd{lowerCI,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{lines}\hlstd{(x, confInt}\hlopt{$}\hlstd{upperCI,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{lines}\hlstd{(}\hlkwd{range}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwd{range}\hlstd{(}\hlkwd{predict}\hlstd{(fitBio16cva)),} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{points}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{= primShade0,}
    \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
  \hlcom{# Overlap between latitude predictors and phenotype predictors}
  \hlstd{imp2} \hlkwb{<-} \hlstd{climVars[vsurfPC1}\hlopt{$}\hlstd{varselect.pred]}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'vsurfPC1' not found}}\begin{alltt}
  \hlstd{nImpPC1} \hlkwb{<-} \hlkwd{length}\hlstd{(imp2)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'imp2' not found}}\begin{alltt}
  \hlstd{vsurfLat}\hlopt{$}\hlstd{varselect.pred}
\end{alltt}
\begin{verbatim}
##  [1] 45 43 42 20 47 41 46 39 19 13
\end{verbatim}
\begin{alltt}
  \hlstd{imp1} \hlkwb{<-} \hlstd{climVars[vsurfLat}\hlopt{$}\hlstd{varselect.pred]}
  \hlstd{nImpLat} \hlkwb{<-} \hlkwd{length}\hlstd{(imp1)}

@@

        \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, nImpLat),}
                \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
        \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Climate-Trait PC1\textbackslash{}nImportance"}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlstd{(nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{)))}
        \hlstd{\{}
                \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{100}\hlstd{,} \hlnum{100}\hlstd{),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
        \hlstd{\}}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'nImpPC1' not found}}\begin{alltt}
        \hlkwd{points}\hlstd{(vsurfPC1}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlstd{nImpPC1], nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{),}
                \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in points(vsurfPC1\$ord.imp\$x[1:nImpPC1], nImpLat:(nImpLat - nImpPC1 + : object 'vsurfPC1' not found}}\begin{alltt}
        \hlcom{# mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, }
  \hlcom{#  at = nImpLat:(nImpLat - nImpPC1 + 1), }
        \hlcom{#	font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{,} \hlnum{0.1}\hlstd{))}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\end{kframe}
\end{knitrout}
